---
title: "presentation"
author: "maisam"
date: "5/30/2020"
output: slidy_presentation
theme : sandstone
highlight : pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of the assignment for week 4 of Developing Data Products course from Coursera (https://www.coursera.org/learn/data-products). It is meant to describe and pitch information about an app developed through Shiny to help property investors determine profitability of a specific property they are interested in investing in

## Application

1)In the application, anyone who is interested in purchasing property for investment purposes can input the purchase price or market value of a property and derive a range of weekly rents necessary to make a profit on the property. The output is generated through calculations programmed in R.

2)The application allows users to include associated costs for owning property that might affect profitability like water usage and community fees (taxes).

3) THe application can be found here :https://mraza8149.shinyapps.io/new_assignment/ 


## Example R Code

```{r  echo=TRUE}
rent<-350
water<-50
fees<-10
mortgage<-200
  result <- (rent * 52 - (water) * 4 - fees * 52 - mortgage * 52) / 52
  return(round(result, digits = 2))
```

## Conclusion

This app can be a very useful tool for property investors looking to do a quick calculation to deterine profitability. The github repository containing the Shiny programs (ui.R and server.R) are found here: https://github.com/maisam8149/developing-data-products
