---
title: "assignment 4"
author: "maisam"
date: "5/28/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Reproducible Pitch

This is a task for the data science coursera course about developing data products for week 4. As part of this, I have created a shiny app and deployed it on the shiny server. The link is https://mraza8149.shinyapps.io/assignment/ . The code can be found at https://github.com/maisam8149/developing-data-products.


## Overview

The shiny app plots graph against miles per gallon (mpg) for different variables from the mtcars dataset.

## Slide with R Output

```{r cars, echo = TRUE}
head(mtcars)
```

## UI CODE

```{r eval=FALSE,echo = TRUE}
library(shiny)

shinyUI(fluidPage(

    # Application title
    titlePanel("Cars Dataset - Miles per Gallon"),
    
    sidebarPanel(
        
        selectInput("variable", "Variable:", 
                    c("Cylinders" = "cyl",
                      "Transmission" = "am",
                      "Gears" = "gear"))
    ),
    
    mainPanel(
        # Output: Formatted text for caption ----
        h3(textOutput("caption")),
        
        # Output: Plot of the requested variable against mpg ----
        plotOutput("mpgPlot")
    )
        
    ))

```

## Server CODE

```{r eval=FALSE,echo = TRUE}

library(shiny)
library(plotly)

mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
shinyServer(function(input, output) {

    formulaText <- reactive({
        paste("mpg vs ", input$variable)
    })
    
    output$caption <- renderText({
        formulaText()
    })
    
    output$mpgPlot <- renderPlot({
        ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
    })
    
})

```